The Resurgence of the Linear Optics Interferometer --- Recent Advances \& Applications

### 2017-04-26 paper.tex
Added to single-photon source section.

In SPDC, a nonlinear crystal with a large $\chi^{(2)}$ is pumped with a strong 
laser and with a small probability, the pump beam is absorbed by the crystal to 
produce two beams of lower energy known as the signal and idler beams. Owing to 
conservation of energy and momentum, the two beams have spatio-temporal 
correlations that can be engineered to produce twin-beam states which have 
perfectly correlated photon numbers. If a single photon were to be detected in one 
of the beams, and then it is certain that the other beam would be in the state of a 
single photon. Some commonly used nonlinear crystals for SPDC are beta barium 
borate (BBO), periodically poled lithium niobate (PPLN), and periodically poled 
potassium titanyl phosphate (PPKTP). Recently, techniques using bismuth triborate 
(BiBO) have improved to the extent of becoming one of the record-holders of single-
photon production.
\cite{bib:WangChen16}.

>>>>

In SPDC, a nonlinear crystal with a large $\chi^{(2)}$ is pumped with a strong 
laser and with a small probability, the pump beam is absorbed by the crystal to 
produce two beams of lower energy known as the signal and idler beams. Owing to 
conservation of energy and momentum, the two beams have spatio-temporal 
correlations that can be engineered to produce twin-beam states which have 
perfectly correlated photon numbers. If a single photon were to be detected in one 
of the beams, and then it is certain that the other beam would be in the state of a 
single photon. Some commonly used nonlinear crystals for SPDC are beta barium 
borate (BBO), periodically poled lithium niobate (PPLN), and periodically poled 
potassium titanyl phosphate (PPKTP). Recently, techniques using bismuth triborate 
(BiBO) have improved to the extent of becoming one of the record-holders of single-
photon production \cite{bib:WangChen16}.

\sihui{ Discuss architectures for producing entangled photon states like GHZ, maybe here or in a different subsection.}

Solid-state single photon sources come from semiconducting nanostructures and 
nitrogen valencies (NV) centers in diamond. Both types are versatile and efficient 
sources of single photons, however the photons they produce have suffered from lack 
of indistinguishability that is necessary for quantum information processing.
Recent developments in the former show promising developments. Notably, a scheme has 
been developed using laser pulses to excite an electronic resonance of a 
semiconducting quantum dot to trigger the emission of single photons 
\cite{bib:Muller07,bib:Vamivakas09, bib:Flagg09,bib:Ates09, bib:Dirk10,
bib:1748,bib:Jayakumar13,bib:Wei14,bib:Muller14,bib:Unsleber15,bib:Ding16,bib:237403,bib:Sweeney14}. Then by embedding the quantum dot in a 
micropillar cavity that has the same resonant frequency as the dot, the scheme
exploits the Purcell effect to achieve higher single-photon production efficiency. 
Such resonant excitation of quantum dots overcome the homogenous broadening of the 
excited state that causes degradation of photon purity and hence 
indistinguisnability.
